\textbf{Appendix}\\ Step by Step: Using Integrated Step Selection Analysis to Simulate Wild Dog Dispersal and Assess Landscape Connectivity

### 2021-06-24 Chapter_2/04_Manuscript/Manuscript_Support.tex
various updates

%------------------------------------------------------------------------------
%	Appendix S2: Evolution of Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Evolution of Heatmaps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.88\textwidth]{99_HeatmapsIndividual.png}
    \caption{Heatmaps produced after 125, 500, and 2000 simulated steps,
    respectively. The left panel (a1, a2, a3) was generated based on simulations
    initiated within the main study area, the right panel (b1, b2, b3) was
    generated based on simulations initiated within the buffer area. To produce
    the heatmap presented in the main text, we summed up values from maps a3 and
    b3.}
    \label{Trajectories}
  \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S3: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Evolution of Betweenness}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.88\textwidth]{99_BetweennessIndividual.png}
    \caption{Maps of betweenness scores produced after 125 (a), 500 (b), and
    2000 (c) simulated steps, respectively. A high betweenness score indicates
    that the respective area is paramount for linking other regions in the study
    area. It therefore highlights movement corridors that provide access to
    various destinations.}
    \label{Trajectories}
  \end{center}
\end{figure}
\restoregeometry

>>>>

%------------------------------------------------------------------------------
%	Appendix S2: Convergence
%------------------------------------------------------------------------------
\newpage
\section{Convergence}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = \textwidth]{99_Convergence.png}
    \caption{}
    \label{Trajectories}
  \end{center}
\end{figure}

%------------------------------------------------------------------------------
%	Appendix S3: Evolution of Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Evolution of Heatmaps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.88\textwidth]{99_HeatmapsIndividual.png}
    \caption{Heatmaps produced after 125, 500, and 2000 simulated steps,
    respectively. The left panel (a1, a2, a3) was generated based on simulations
    initiated within the main study area, the right panel (b1, b2, b3) was
    generated based on simulations initiated within the buffer area. To produce
    the heatmap presented in the main text, we summed up values from maps a3 and
    b3.}
    \label{Trajectories}
  \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S4: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Evolution of Betweenness}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.88\textwidth]{99_BetweennessIndividual.png}
    \caption{Maps of betweenness scores produced after 125 (a), 500 (b), and
    2000 (c) simulated steps, respectively. A high betweenness score indicates
    that the respective area is paramount for linking other regions in the study
    area. It therefore highlights movement corridors that provide access to
    various destinations.}
    \label{Trajectories}
  \end{center}
\end{figure}
\restoregeometry

\section{Step Selection Summary}
Resource Selection Functions (RSFs) and Resource Selection Probability Functions
(RSPFs) are routinely used to model habitat selection by animals using data from
Very High Frequency (VHF) and Global Positioning System (GPS) locations. A
RS(P)F is defined as any statistical model deployed to estimate the relative
probability of selecting a resource unit versus alternative possible resource
units \citep{Manly.2002}.

Compared to a RSF, a RSPF yields the actual probability that an available
resource unit is selected and can be estimated using weighted distribution
theory \citep{Lele.2006}.

Compared to RSFs, the key feature of SSFs is link- ing consecutive animal
locations (most commonly taken at regular time intervals) that can be defined as
steps \citep{Turchin.1998} (Figure 1).

With step selection functions, GPS trajectories are broken down into steps, each
representing the straight line segment between two consecutive GPS relocations.
Each observed step is then paired with a set of random steps, having the same
starting point but differing in length and orientation \citep{Fortin.2005}. To
sample step lengths and orientations (i.e. turning angles), \cite{Fortin.2005}
sampled values from observed steps. Later studies, on the other hand, rely on
parametrized distributions, fitted to observed steps. By comparing
characteristics at observed and random steps using conditional logistic
regression, features influencing elk movements can be determined. The step
selection function takes the form \citep{Fortin.2005}:

\begin{equation}
\label{EQ1}
\hat{w}(x) = exp(\beta_1 x_1 + \beta_2 x_2 + \beta_3 x_3 + ... + \beta_n x_n)
\end{equation}

Where coefficients \(\beta_1\) to \(\beta_n\) are estimated using conditional
logistic regression and are associated with environmental covariates \(x_1\) to
\(x_n\), respectively. Ultimately, steps with higher \(\hat{w}(x)\) have higher
\textbf{odds} of being chosen.

As the time interval between relocations increases, it can be expected that
autocorrelation in the data decreases.

How to state results:
\begin{itemize}
  \item  Assuming that other environmental factors remain constant, animals were
  less likely to ...
  \item Animals generally avoided steps in areas made up of a large proportion
  of ...
  \item  An increase in ... did not generally decrease the odds of animals
  choosing these steps, as indicated by the positive association between ... and
  the probability of animals making steps covering the two most widely available
  vegetation cover types
\end{itemize}
